---
title: "How to orginze perfect lottery where people never win anything - Amino KasaRomana"
author: "Maciej Nasinski"
date: "`r Sys.Date()`"
output: 
  html_document:
    fontsize: 12pt
    spacing: double
    fig_caption: yes
    indent: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In Poland there is a very popular lottery organized by a Amino food company named Kasa Romana.   
It was established first time in 90's and the last attempt known by me in the 2016.  
There were gathered a sufficient data about it because of the YouTube channel which testing certain products in thousands during some promations.  
[BezKanalu YouTube channel](https://www.facebook.com/BezKanalu/) brought precisely 1002 coupons from last event.   
The main objectives are to find patterns for this data and make sure if the coupons give any chance to win some real money.  
The main rule is that people could win money if the have a set of coupons which sum to full hundreds (100, 200, ...) up to 1000.  
The knapsack algorithm was used to check if there are some combinations of coupons which enable to win some money.  
All processing is done from R programming environment.  

Loading the data:

```{r}
coupons = as.numeric(readLines("./knapsack.txt"))

head(coupons, 30)
```


Sorted table of frequencies:

```{r}
sort(table(coupons))
```

Histrogram might be helpful to find certain patterns:

```{r}
hist(coupons,breaks=100)
```

**Numbers seems to be generated from 2 specific patterns:**

- multiplication of 13 starting from 26
- multiplication of 13 plus 165

```{r}
rep13 = sapply(1:52, function(x) 13*x)

rep2_13 = sapply(0:45, function(x) 165 + (13*x))

all(coupons %in% c(rep13, rep2_13))
```

All of our coupons comes from this 2 sequences.

Compering coupons with artificially generated ones form two presented sequences.

```{r}
a = sort(c(unique(coupons),178)) # one coupon has to be added 165 + 13
b = sort(c(sapply(0:45,function(x) 165+(13*x)),sapply(2:50,function(x) (13*x))))

both = data.frame(real = a, generated = b)

head(both)

tail(both)
```

*Single knapsack problem:*

Knapsack is an optimization method, linear programming for integers.

Each of 1000 coupons is replicated 100 times before the procedure. This replication step is not needed to get this certain results although it will be even more clear. Remainder we looking for set of coupons which sum to full hundreds (100, 200, ...) up to 1000.

```{r}
library(adagio)

cupon_we_have = rep(both$generated,100)

cupon_we_want = seq(100,1000,100)

for(i in cupon_we_want){

solution <- try(knapsack(p=cupon_we_have[cupon_we_have<i], w=cupon_we_have[cupon_we_have<i], cap=i))

print(solution$profit)
}

```

Taking into account only coupons provided there is no chance to win anything.  
This seems to no be surprising when we know from what sequences the coupons come from.  
The question is about potential existence of other coupons which might enable to win something.  


```{r, echo = FALSE, eval = FALSE}
set.seed(1234)

cupon_we_have = round(c(runif(1000,26,750)))

hist(cupon_we_have,10)

cupon_we_want = 1000

prof = 0

repeat{

solution <- try(mknapsack(p=cupon_we_have, w=cupon_we_have, k=cupon_we_want,bck=0))

if(class(solution)=="try-error") break

diff = NULL

for(i in 1:length(cupon_we_want)) diff[i] = cupon_we_want[i] - sum(cupon_we_have[solution$ksack==i])

if(all(diff==0)) cupon_we_want = c(cupon_we_want,1000) else break

prof = prof + 1
}

c = cupon_we_have
names(c) = solution$ksack
c = c[sort(as.numeric(names(c)),index.return=TRUE)$ix]
c = c[!names(c)==0]
c
```
